\chapter*{Acknowledgements}
\chaptermark{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
At first I want to thank Achille Stocchi for giving me the opportunity of doing my master's thesis at 'his' LAL, especially since there is no such thing as a master's thesis in particle physics in France. I also want to thank you for allowing me to participate in the NPAC masters where I applied much to late during my ERASMUS year in Paris. It was the participation in this program that permitted me to meet the \lhcb group. And I want to thank you for persuading Marie-H\'{e}l\`{e}ne Schune to take me as an intern even though I had set to my mind to follow the German master's system.\\
\\
I want to thank my supervisor Marie-H\'{e}l\`{e}ne Schune \textbf{very very much} for teaching more than I thought was possible and for showing me this incredibly amazing world of of ideas and scientific forward-thinking that is particle physics. I will be eternally grateful for all the effort that was put into my training and all the mistakes I made that were immediately forgiven, even if at least one of them almost broke both our hearts. Thank you for giving me confidence in myself and my capabilities and for being so supportive even after I decided to leave. And of course thank you for supplying me with sweets.\\
I also want to thank Jacques Lefrancois for the long discussions about bremsstrahlung, polarisation and photon conversion. I have learned a lot, especially that experimental physicists also can have a descent amount of theoretical knowledge. And I also enjoyed these discussions and enjoyed seeing all the connections and how to derive them. I am stilled awed by the amount of knowledge you posses.\\
Before I continue with thanking individual people, I want to thank the entire \lhcb group at LAL. Everybody has been very kind and welcoming right from the start and while this might seem natural to some I know that that's not the way it is done everywhere. Thank you for being so very willing to help and for including everyone into the group right from the start.\\
\\
Next I want to thank Alexandra for being my office mate and a very good help when it comes to making beautiful plots in \roofit. I enjoyed our little singing sessions and our tee-times very much. Thank you for calling me ''little bunny'', you are truly a bunny yourself.
It was very cushy to have someone going trough the (masters) thesis craziness with me and sharing some nice chocolate in time of stress. I wish you that you'll find some awesome jobs that also makes a lot of money and then you can buy some bunnies and think of me. \\
I want to thank Alexis for always being somehow cheerful and for making me say very inappropriate words during lunch at CESFO. I will definitely call you if somebody in Bristol is mean to me!\\
I want to thank Frederic for his frog-story during \lhcb week in Davos that I will never ever forget.\\
I want to thank Benoit for his countless stories that were often told so fast that I had to extrapolate between bits that I understood. I hope I will not spread false stories about what you said.\\
Of course I also want to thank Chris for all the food he provided while I resided in Aachen. Very delicious indeed! And thanks also for the moral support during the entire thesis.\\
Tine! Thanks for suffering with me and even more! And thanks for watching and sending me pictures of baby animals when nothing else was working. Also thanks a lot for being the link between me and the Aachen-world. I am pretty sure many things -- like my final presentation -- would not have worked without you. Thanks for not letting me hang out to dry in France but for giving me the all the intel, you are my favourite spy! I always have our plan-b in mind and that reassures me, that even if all fails I can still live on a bunny-pony farm somewhere where it's warm and cosy.\\
I also want to thank Djalel for the endless discussions about \bdts, philosophy, psychology and sociology. They have been very enlightening and I enjoyed them a great deal. I will truly miss them.\\
Frank, thank you for reading over this master's thesis even though it is not your area of expertise at all. Your comments have been very helpful.\\
I also want to thank Jibo for his immense help with all \davinci related topics even after he left the group. I don't know what we would have done  without you! Somehow the 10 minutes rule has been burned into my brain and I will apply it all my life.\\
Of course I want to thank Lo and Heiner for answering my countless questions about CMS. You were incredibly helpful and also fun of course.\\
Martino, now it's up to you to make an amazing angular analysis. I am counting on you! Stay funny and panic once in a while since this somehow seems to calm me down.\\
Michelle! Thanks a lot for the electrons and for sharing some of my dislikes. This has cheered me up and given me back faith into my mental sanity. I have enjoyed our pizza and wine evenings and while I am sitting here all alone in the middle of the night I wish somebody would bring me a creme fresh champignon pizza! and just in case Bristol does not work out I hope you still have some space on your roof terrace.\\
Thank you Patrick, for being a very quite co-buero and for tolerating all my unusual eating and working habits. I have enjoyed all your posters in the office and I will hang some in my new office.\\
Great thanks goes to Paul who read my master's thesis more meticulously than everybody else. Your scanning skills must be amazing. I am also very happy about your helpful comments, you truly deserve a big cake.\\
I want to thank Philipp 'The Panda' for the occasional passing on of letters and bills that should have been paid months ago. Your authenticity is inspiring and you are indeed my favourite panda.\\
To Thiemo just as he wished for (even though he could have gotten something better):Thank you!\\
Thanks to Sam and Andrew for their help with English expressions even if I was surprised about how difficult that seemed. \\
Sergey, thanks for the Ukrainian chocolate things that were so sweet they made my mouth burn. And thank you for telling me to go home once in a while even if I didn't listen.\\
Thanks Vagelis for not one but even two afternoon coffees and for always staying positive even if I wanted to see only the negative.\\
\\
Actually I want to thank everybody who contributed in brining me where I am right now, this master's thesis would not have been possible without you. Starting with my parents that taught me to be tough and to work hard and my grand-parents who told me that sometimes being soft is ok too, to my physics teacher in school that believed in me and told me that I was energetic enough to study physics with (or against) the male competition. Of course everything would not have been possible without all my friends who made studying physics not only possible but also fun. Thank every single one of you for all the talks and the fun we had.\\
\\
Overall I am thankful for everybody I met during my master's thesis and everything that I could learn -- be it professional or private. I wish you all the super duper best and I will miss you. See you at \cern or in Bristol or in Paris or in any other place of the world!